---
title: "Knapsack"
author: "Clara Schartner and Araya Eamrurksiri"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The package  `Knapsack` includes functions which are implementations of different algorithm towards solving the Knapsack problem.

- `brute_force_knapsack` 
- `greedy_knapsack`
- `dynamic_knapsack`



## Background

The knapsack problem is a discrete optimization problem where we have a knapsack that can take a
limited weight W and we want to fill this knapsack with a number of items i = 1, ...,n, each with a weight wi and a value $v_{i}$. The goal is to find the knapsack with the largest value of the elements addedto the knapsack.


## Examples

First you have to load the library knapsack.

```{r}
library(knapsack)
```
Then you have to construct a dataframe of the right sizes to input.
The dataframe has to have a column with the weight of each object and a column with the value of it.
```{r}
set.seed(42)
n <- 2000
knapsack_objects <-data.frame(w=sample(1:4000, size = n, replace = TRUE),v=runif(n = n, 0, 10000))
```
The three different functions solve this problem in a different way.
But the input is always the same: First a dataframe with the weights and value and a threshold for the weight.
```{r}
greedy_knapsack(x=knapsack_objects[1:8,],W=3500)
```


```{r}
knapsack_dynamic(x=knapsack_objects[1:4,],W=3500)
```


```{r}
brute_force_knapsack(x=knapsack_objects[1:8,],W=3500)
```
## Further features


The function `par_brute_force_knapsack` allows you to specify to parallelize some computations.

Since the `brute_force_kanpsack` is computationally expensive the function `par_brute_force_knapsack` was written, which allows you to parallelize it.
This function works only on Windows.
```{r}
par_brute_force_knapsack(x=knapsack_objects[1:8,],W=3500,par=TRUE)
```

##Answers

```{r,echo=FALSE}
#library(knapsack)
set.seed(42)
n <- 1000000
knapsack_objects <-data.frame(w=sample(1:4000, size = n, replace = TRUE),v=runif(n = n, 0, 10000))
```

```{r}
system.time(old_brute_force_knapsack(knapsack_objects[1:16,],W=2000))
```
The performance gained by a few improvements is quite large as can be seen.
```{r}
system.time(brute_force_knapsack(knapsack_objects[1:16,],W=2000))
```

```{r}
system.time(knapsack_dynamic(knapsack_objects[1:500,],W=2000))
```

```{r}
system.time(greedy_knapsack(knapsack_objects[1:1000000,],W=2000))
```

